Paper Five Summary

### 2015-10-18 hw/read/5/summary.tex
Added conway's law
Conway's law
Connection to other papers

\section*{Important Keywords}
\begin{description}
\item [{Organizational metrics}] Metrics designed to give a balanced view of organizational complexity with respect to software development. The authors argue that these metrics, as a measure of organizational structure, greatly affect product quality.
\item[{Failure-proneness}] The probability that a particular piece of software will fail in production. The authors hope to reduce this by incorporating organizational metrics into models.
\item[{Software Metrics}]  The authors define them as things like code churn, code complexity, code coverage, and code dependencies.  These metrics have been used to determine fault proneness.
\end{description}

@@

>>>>

\section*{Important Keywords}
\begin{description}
\item [{Organizational metrics}] Metrics designed to give a balanced view of organizational complexity with respect to software development. The authors argue that these metrics, as a measure of organizational structure, greatly affect product quality.
\item[{Failure-proneness}] The probability that a particular piece of software will fail in production. The authors hope to reduce this by incorporating organizational metrics into models.
\item[{Software Metrics}]  The authors define them as things like code churn, code complexity, code coverage, and code dependencies.  These metrics have been used to determine fault proneness.
\item[{Conway's Law}] Organizations that design systems are constrained to produce the systems which are copies of the communication structures of these organizations.

@@

In \cite{bird09}, this paper was referenced by the authors as previous research.  The organizational metrics described in this paper were used as a set of features in \cite{bird09}. It was also used in that paper to reinforce the conclusion that organizationally distributed development affects the number of post-release defects.
